\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 setobook.tex
Activated section numbering
Set section numbering depth to 1 (instead of initial -1)
updates to intro etc
heading changes based on Minh and discussion; also noted FP comments
minor fix to acknowledgements.

\title*{\textbf{\sc Towards Deliberative Control in Marine Robotics}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \emph{\{Kanna.Rajan,fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \emph{javier.barreiro@nasa.gov}}

@@

Rajan and Py are funded by a block grant from the David and Lucile
Packard Foundation to MBARI. They thank their collaborators J. Ryan,
J. Harvey, R. Vrijenhoek and J. Bellingham at MBARI. In addition they
thank colleagues M. del Alto, D. Korsmeyer and S. Zornetzer at NASA
Ames who made \eu available as open source. The authors are indebted
to N. Muscettola for his ideas and early work at NASA Ames which forms
the basis of this work.

>>>>

\title*{\textbf{\sc Towards Deliberative Control in Marine Robotics}}
\author{\normalsize Kanna~Rajan\inst{1} \and Fr\'ed\'eric Py\inst{1}
  \and Javier Barreiro\inst{2}}
\institute{Monterey Bay Aquarium Research Institute, California
  \emph{\{Kanna.Rajan, fpy\}@mbari.org}
  \and
  NASA Ames Research Center, Moffett Field, California
  \emph{javier.barreiro@nasa.gov}}

@@

Rajan and Py are funded by a block grant from the David and Lucile
Packard Foundation to MBARI. They thank their collaborators John Ryan,
Julio Harvey, Jim Bellingham and Robert Vrijenhoek at MBARI. In
addition they thank colleagues Martha del Alto, David Korsmeyer and
Steven Zornetzer at NASA Ames who made \eu available as open
source. The authors are indebted to Nicola Muscettola for his ideas
and early efforts in Constraint-based Temporal Planning at NASA Ames
which forms the basis of this work.
The authors also want to thank everybdy who has contributed to the 
development of \eu and its online documentation over the years, specially Ari Jonsson, Jeremy Frank, Conor McGann, Paul Morris,
Michael Iatauro, Matthew Boyce and Tristan Smith.
